Interisland movements of woodland caribou in Newfoundland

### 2020-02-19 paper/manuscript.Rmd
Update manuscript.Rmd and manuscript.md

Here, we describe the visual observation of an adult male caribou swimming
between islands in the Fogo Island archipleago in the North Atlantic Ocean.
During routine fieldwork on May 30, 2017, we observed an unmarked adult male
caribou swim between Perry and Eastern Indian Islands (Figure 1), a swim of at
least 470 m which took ~9 minutes (~52 m per minute). This observation prompted
us to query a large database of GPS radio-collared caribou in the Fogo Island
caribou herd in Newfoundland, Canada. We identified  86 remotely sensed swimming
events between XX islands from three individual caribou over a three-year
period.

@@

The Fogo Island archipelago is located in Newfoundland, Canada (49°N, 54°W), and
comprises approximately ten islands. While Fogo Island is the largest island
(237.71 km^2), the archipelago includes at least three larger islands: Western
Indian (77.6 km2), Eastern Indian (38.7 km2) and Change (XX km2) Islands, as
well as numerous smaller islands, including Blundon’s (1.18 km2), North Long
(1.01 km2), South Long (0.48 km2), Kate’s (1.64 km2), and Brother’s (1.59 km2)
Islands (see Figure 1). All islands in the Fogo Island archipelago consist
largely of coniferous and mixed forests of balsam fir (Abies balsamea), black
spruce (Picea mariana), and white birch (Betula payrifera) as well as bogs,
lakes, lichen and rocky barrens.

>>>>

Here, we describe the visual observation of an adult male caribou swimming
between islands in the Fogo Island archipleago off the coast of Newfoundland,
Canada. During routine fieldwork on May 30, 2017, we observed an unmarked adult
male caribou swim between Perry and Eastern Indian Islands (Figure 1), a swim of
at least 470 m which took ~9 minutes (~52 m per minute). This observation
prompted us to query a large database of GPS radio-collared caribou. We
identified  86 remotely sensed swimming events between XX islands from three
individual caribou over a three-year period.

@@

The Fogo Island archipelago is located in Newfoundland, Canada (49°N, 54°W), and
comprises approximately ten islands. While Fogo Island is the largest island
(237.71 km^2^), the archipelago includes at least three larger islands: Western
Indian (77.6 km2), Eastern Indian (38.7 km2) and Change (XX km2) Islands, as
well as numerous smaller islands, including Blundon’s (1.18 km2), North Long
(1.01 km2), South Long (0.48 km2), Kate’s (1.64 km2), and Brother’s (1.59 km2)
Islands (see Figure 1). All islands in the Fogo Island archipelago consist
largely of coniferous and mixed forests of balsam fir (Abies balsamea), black
spruce (Picea mariana), and white birch (Betula payrifera) as well as bogs,
lakes, lichen and rocky barrens.
